%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% "ModernCV" CV and Cover Letter
% LaTeX Template
% Version 1.11 (19/6/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Xavier Danaux (xdanaux@gmail.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important note:
% This template requires the moderncv.cls and .sty files to be in the same 
% directory as this .tex file. These files provide the resume style and themes 
% used for structuring the document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[12pt,a4paper,sans]{moderncv} % Font sizes: 10, 11, or 12; paper sizes: a4paper, letterpaper, a5paper, legalpaper, executivepaper or landscape; font families: sans or roman

\moderncvstyle{casual} % CV theme - options include: 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{green} % CV color - options include: 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'

\usepackage{lipsum} % Used for inserting dummy 'Lorem ipsum' text into the template

\usepackage[scale=0.75]{geometry} % Reduce document margins
%\setlength{\hintscolumnwidth}{3cm} % Uncomment to change the width of the dates column
%\setlength{\makecvtitlenamewidth}{10cm} % For the 'classic' style, uncomment to adjust the width of the space allocated to your name

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION SECTION
%----------------------------------------------------------------------------------------

\firstname{Zhi} % Your first name
\familyname{Yang Ph.D} % Your last name
% All information in this block is optional, comment out any lines you don't need
\title{Professor of Cognitive Neuroscience \\ \\ Beijing An-Ding Hospital, Capital Medical University}
\address{Webpage}{https://www.researchgate.net/profile/Zhi-Yang-24/research}
%\mobile{(+86)18611710840}
\email{yangz@mail.ccmu.edu.cn}


%\photo[70pt][0.4pt]{pictures/picture} % The first bracket is the picture height, the second is the thickness of the frame around the picture (0pt for no frame)
%\quote{Laboratory of Psychological Health and Imaging,\\Shanghai Mental Health Center,\\Shanghai Jiao Tong University, Medical School;\\ \\ \\Institute of Psychological and Behavioral Sciences,\\Shanghai Jiao Tong University}

%----------------------------------------------------------------------------------------

\begin{document}
\makecvtitle % Print the CV title

\section{Research Interests}
\cvitem{}{\textbf{Neuroimaging and Non-invasive Brain Modulation of Mental Disorders}}
\cvitem{}{\textbf{Brain development and child/adolescent psychiatry}}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\cventry{2003--2008}{Ph.D., Cognitive Neuroscience}{Institute of Psychology, Chinese Academy of Sciences}{Beijing, China}{\textit{Cognitive Neuroscience}}{Thesis: Reproducibility-based Independent Component Analysis for fMRI data}  % Arguments not required can be left empty
\cventry{2005--2007}{Visiting Student}{Emory University}{Atlanta, GA, USA}{\textit{Department of Biomedical Engineering}}{Advisor: Dr. Xiaoping P. Hu}
\cventry{1999--2003}{B.S., Biomedical Engineering}{Tsinghua University}{Beijing, China}{\textit{Department of Electrical Engineering}}{}

%------------------------------------------------

%\subsection{PROJECT}

%\cventry{2015}{Foot Step Power Generation by Piezoelectric Material}{Live Project.}{}{}{This is basically a Live Project. The main theme of the project is to generate power by applying pressure on piezoelectric material with the help of non-renewable resources like foot step and other.}

%----------------------------------------------------------------------------------------
%	Professional History
%----------------------------------------------------------------------------------------

\section{Professional History}
\cventry{2023 - Present}{Professor, Director}{Beijing An-Ding Hospital, Capital Medical University}{Beijing, China}{}{Role: Director of Neuroimaging Division, National Research Center for Mental Disorders; Ph.D student supervisor}
\cventry{2018--2023}{Professor}{Institute of Psychological and Behavioral Sciences, Shanghai Jiao Tong University}{Shanghai, China}{}{Role: teaching graduate and undergraduate course of cognitive neuroscience; Ph.D student supervisor}
\cventry{2018--2024}{Executive Director}{Neuroimaging Data Center, Shanghai Mental Health Center}{Shanghai, China}{}{Role: leading a team to develop, manage and maintain a neuroimaging center}
\cventry{2017--2023}{P.I. of Laboratory of Psychological Health and Imaging}{Shanghai Mental Health Center}{Shanghai, China}{}{Role: Leading a team in cognitive neuroscience research on mental disorders}
\cventry{2015-2018}{Professor}{University of Chinese Academy of Sciences}{Beijing, China}{}{Role: teaching courses of cognitive neuroscience}
\cventry{2012-2017}{Associate Professor}{Institute of Psychology, Chinese Academy of Sciences}{Beijing, China}{\textit{Laboratory of Cognition and Development}}{Role: conducting cognitive neuroscience research}
\cventry{2012-2014}{Senior Research Fellow}{National Institutes of Health}{Bethesda, MD, USA}{\textit{Section on Functional Imaging Methods}}{Role: conducting cognitive neuroscience research}
\cventry{2008-2012}{Assistant Professor}{Institute of Psychology, Chinese Academy of Sciences}{Beijing, China}{\textit{Laboratory of Cognition and Development}}{Role: conducting cognitive neuroscience research}

%----------------------------------------------------------------------------------------
%	Funds
%----------------------------------------------------------------------------------------

\section{Research Funds}
\cventry{2025-2028}{Regular Project (82471576), National Natural Science Foundation of China}{Context-dependent multi-network brain stimulation: A precision approach for social anxiety disorder}{Role: PI}{CNY 588,000}{}

\cventry{2020-2023}{Regular Project (81971682), National Natural Science Foundation of China}{Individualized diagnosis of mental disorders based on cross-disease neuroimaging database}{Role: PI}{CNY 660,000}{}

\cventry{2016-2019}{Regular Project (81571756), National Natural Science Foundation of China}{Detecting subtypes of schizophrenia using neuroimaging under natural stimulus}{Role: PI}{CNY 672,000}{}

\cventry{2013-2016}{Renewed Regular Project (81270023), National Natural Science Foundation of China}{The specificity of the neuroimaging biomarkers for mental disorders}{Role: PI}{CNY 700,000}{}

\cventry{2010-2012}{Young Investigator Project (30900366), National Natural Science Foundation of China}{Data-driven neuroimaging marker research on classification of mental disorders}{Role: PI}{CNY 210,000}{}

\cventry{2025-2027}{Research Ward Excellence Program (BRWEP2024W072120106), Beijing Municipal Health Commission, China}{Intelligent optimization of neural modulation of depression based on contextual neuroimaging}{Role: PI}{CNY 2100,000}{}

\cventry{2020-2023}{Natural Science Foundation of Shanghai (20ZR1472800)}{Relationships of taste perception and anxiety in adolescents}{Role: PI}{CNY 500,000}{}

\cventry{2015-2017}{Beijing Nova Program (2015079B), Beijing Municipal Commission of Science and Technology}{Neuroimaging biomarkers for mental disorders: methodologies for the big data era}{Role: PI}{CNY 350,000}{}

\cventry{2017-2020}{Gaofeng Clinical Medicine Grant Support (20171929), Shanghai Municipal Education Commission}{Neuroimaging markers for schizophrenia}{Role: PI}{CNY 1,000,000}{}

\cventry{2018-2021}{Hundred-talent Fund (2018BR17), Shanghai Municipal Commission of Health}{Brain development abnormality in social anxiety disorder}{Role: PI}{CNY 900,000}{}

\cventry{2015-2019}{Youth Innovation Foundation, Chinese Academy of Sciences}{}{Role: PI}{CNY 400,000}{}

\cventry{2014-2019}{Outstanding Young Investigator Award, Institute of Psychology, Chinese Academy of Sciences}{Data-ming framework for brain network informed subject community detection}{Role: PI}{CNY 400,000}{}

%----------------------------------------------------------------------------------------
%	Publication
%----------------------------------------------------------------------------------------
\section{Peer-Reviewed Publications (Selected)}
\cvitem{}{Zang Z, Li A, Zhang Z, Wu T, Chen X, Qiao K, Paerhati A,  \textbf{\underline{Yang Z*}}, Wang G* (2025): Intranasal (R)-ketamine modulates depression symptom and neurotransmitters-associated human brain connectivity. \emph{Neurotherapeutics}, DOI:10.1016/j.neurot.2025.e00790}

\cvitem{}{Mao B, Zhang H, Wang H, \textbf{\underline{Yang Z*}} (2025): Mapping early corpus callosum development to identify neurodevelopmental risk. \emph{Dev Cogn Neurosci}, DOI:10.1016/j.dcn.2025.101605}

\cvitem{}{Li Q, Wang W, Guo Q, Jiang L, Qiao K, Hu Y, Zhang X, Wang Z, Peng D, Fan Q, Zhao M, Fang Y, Wang J, Qiu H, Wang J, Li G*, Sheng J*, Tang Y, Jin C, Shen D, Niznikiewicz M, Li C, \textbf{\underline{Yang Z*}} (2025): Towards neuroimaging-based diagnostic support: A deep learning approach with a closed-loop system for psychiatric classification. \emph{iScience}, DOI:10.1016/j.isci.2025.114100}

\cvitem{}{Ding J, Zhang X, Liu J, Hu Z, \textbf{\underline{Yang Z*}}, Tang Y*, Ding Y*(2025): Entrainment of rhythmic tonal sequences on neural oscillations and the impact on subjective emotion. \emph{Sci Rep}, DOI:10.1038/s41598-025-98548-1}

\cvitem{}{Kang Y,  Li Q, Liu W, Hu Y, Liu Z, Xie S, Ma C, Zhang L, Zhang X, Hu Z, Ding Y, Cheng W, \textbf{\underline{Yang Z*}} (2024): Risk factor patterns define social anxiety subtypes in adolescents with brain and clinical feature differences. \emph{J Eur Child Adolesc Psychiatry}, DOI:10.1007/s00787-024-02548-x}

\cvitem{}{Zhang X, Zhou J, Chen Y, Guo L, \textbf{\underline{Yang Z*}}, Robbins T, Fan Q* (2023): Pathological networking of gray matter dendritic density with classic brain morphometries in OCD. \emph{JAMA Network Open}, 6(11):2343208. DOI:10.1001/jamanetworkopen.2023.43208}

\cvitem{}{Xie S, Liu J, Hu Y, Liu W, Ma C, Jin S, Zhang L, Kang Y, Ding Y, Zhang X, Hu Z, Cheng W*, \textbf{\underline{Yang Z*}} (2023): A normative model of brain responses to social scenarios reflects the maturity of children and adolescents’ social-emotional abilities. \emph{Social Cognitive and Affective Neuroscience}, Published Online, DOI:10.1093/scan/nsad062}

\cvitem{}{Sun L*, Li W, Qiu Q, Hu Y, \textbf{\underline{Yang Z*}}, Xiao S* (2023): Anxiety adds the risk of cognitive progression and is associated with axon/synapse degeneration among cognitively unimpaired older adults. \emph{eBioMedicine}, 94:104703. DOI:10.1016/j.ebiom.2023.104703}

\cvitem{}{Liu W, Hu Z, Liu Z, Zhang F, Ding Y, Shui Y, \textbf{\underline{Yang Z*}}, Cheng W* (2023): Age- and sex-dependent increase in self-harm among adolescents with mental health problems in East China during COVID-19 related society-wide isolation. \emph{Frontiers in Public Health}, 11:1129123. DOI:10.3389/fpubh.2023.1129123}

\cvitem{}{Hu Y, Li Q, Qiao K, Zhang X, Chen B, \textbf{\underline{Yang Z*}} (2023): PhiPipe: A multi-modal MRI data processing pipeline with test-retest reliability and predicative validity assessments. \emph{Human Brain Mapping}, 44(5):2062-2084. DOI:10.1002/hbm.26194}

\cvitem{}{Liu J, Xie S, Hu Y, Ding Y, Zhang X, Liu W, Zhang L, Ma C, Kang Y, Jin S, Xia Y, Hu Z, Liu Z, Cheng W*, \textbf{\underline{Yang Z*}} (2023): Age‐dependent alterations in the coordinated development of subcortical regions in adolescents with social anxiety disorder. \emph{European Child \& Adolescent Psychiatry}. DOI:10.1007/s00787-022-02118-z}

\cvitem{}{Jin S, Liu W, Hu Y, Liu Z, Xia Y, Zhang X, Ding Y, Zhang L, Xie S, Ma C, Kang Y, Hu Z*, Cheng W*, \textbf{\underline{Yang Z*}} (2023): Aberrant functional connectivity of the bed nucleus of the stria terminalis and its age dependence in children and adolescents with social anxiety disorder. \emph{Asian Journal of Psychiatry}, 82:103498. DOI:10.1016/j.ajp.2023.103498}

\cvitem{}{Jiang L, Qiao K, Li Q, Hu Y, Zhang X, Wang J, Peng D, Fan Q, Zhao M, Sheng J, Wang J, Li C, Fang Y, Wang Z*, \textbf{\underline{Yang Z*}} (2022): Categorical and dimensional deficits in hippocampal subfields among schizophrenia, obsessive-compulsive disorder, bipolar disorder, and major depressive disorder. \emph{Biological Psychiatry: Cognitive Neuroscience and Neuroimaging.} In press}

\cvitem{}{Zhang H, Li J, Su X, Hu Y, Liu T, Ni S, Li H, Zuo X-N, Fu J*, Yuan T-F*, \textbf{\underline{Yang Z*}} (2022): Growth charts of brain morphometry for preschool children. \emph{NeuroImage} 255: 119178.DOI: 10.1016/j.neuroimage.2022.119178}

\cvitem{}{Zhang Q, Li B, Jin S, Liu W, Liu J, Xie S, Zhang L, Kang Y, Ding Y, Zhang X, Cheng W*, \textbf{\underline{Yang Z*}} (2022): Comparing the Effectiveness of Brain Structural Imaging, Resting-state fMRI, and Naturalistic fMRI in Recognizing Social Anxiety Disorder in Children and Adolescents. \emph{Psychiatry Research: Neuroimaging} 111485. DOI: 10.1016/j.pscychresns.2022.111485}

\cvitem{}{Ding Y, Liu J, Zhang X, \textbf{\underline{Yang Z*}} (2022): Dynamic Tracking of State Anxiety via Multi-Modal Data and Machine Learning. \emph{Frontiers in Psychiatry} 13: 757961. DOI: 10.3389/fpsyt.2022.757961}

\cvitem{}{Hu Y, \textbf{\underline{Yang Z*}} (2021). Impact of inter-individual variability on the estimation of default mode network in temporal concatenation group ICA. \emph{Neuroimage}. 234: 118114. DOI: 10.1016/j.neuroimage.2021.118114}

\cvitem{}{Xie S, Zhang X*, Cheng W, \textbf{\underline{Yang Z}} (2021): Adolescent anxiety disorders and the developing brain: comparing neuroimaging findings in adolescents and adults. \emph{General Psychiatry} 34: e100411. DOI: 10.1136/gpsych-2020-100411}

\cvitem{}{Li Q, Jiang L, Qiao K, Hu Y, Chen B, Zhang X, Ding Y, \textbf{\underline{Yang Z*}}, Li C. (2021): INCloud: integrated neuroimaging cloud for data collection, management, analysis and clinical translations. \emph{General Psychiatry} 34: e100651. DOI: 10.1136/gpsych-2021-100651}

\cvitem{}{Jiang L, Cui H, Zhang C, Cao X, Gu N, Zhu Y, Wang J, \textbf{\underline{Yang Z}}, Li C. (2021): Repetitive Transcranial Magnetic Stimulation for Improving Cognitive Function in Patients With Mild Cognitive Impairment: A Systematic Review. \emph{Frontiers in Aging Neuroscience} 12: 593000. DOI: 10.3389/fnagi.2020.593000. eCollection 2020}

\cvitem{}{Zeng Y, Tao F, Cui Z, Wu L, Xu J, Dong W, Liu C, \textbf{\underline{Yang Z}}, Qin S*. (2021): Dynamic integration and segregation of amygdala subregional functional circuits linking to physiological arousal. \emph{NeuroImage} 238: 118224. DOI: 10.1016/j.neuroimage.2021.118224}

\cvitem{}{Xu Z, Zhang X, Chang H, Kong Y, Ni Y, Liu R, Zhang X, Hu Y, \textbf{\underline{Yang Z}}, Hou M, Mao R, Liu W-T, Du Y, Yu S, Wang Z, Ji M*, Zhou Z*. (2021): Rescue of maternal immune activation-induced behavioral abnormalities in adult mouse offspring by pathogen-activated maternal Treg cells. \emph{Nature Neuroscience} 24(6): 818–830. DOI: 10.1038/s41593-021-00837-1}

\cvitem{}{Gao J, Chen G, Wu J, Wang Y, Hu Y, Xu T, Zuo X-N*, \textbf{\underline{Yang Z*}} (2020). Reliability map of individual differences reflected in inter-subject correlation in naturalistic imaging. \emph{Neuroimage} 223: 117277. DOI: 10.1016/j.neuroimage.2020.117277}

\cvitem{}{Liu Z, Hu Y, Zhang Y, Liu W, Zhang L, Wang Y, Yang H, Wu J, Cheng W*, \textbf{\underline{Yang Z*}} (2020). Altered gray matter volume and structural co-variance in adolescents with social anxiety disorder: evidence for a delayed and unsynchronized development of the fronto-limbic system. \emph{Psychological Medicine} 51(10): 1742-1751. DOI: 10.1017/S0033291720000495}

\cvitem{}{Guo Q, Hu Y, Zeng B, Tang Y, Li G, Zhang T, Wang J, Northoff G, Li C, Goff D, Wang J*, \textbf{\underline{Yang Z*}} (2020). Parietal memory network and default mode network in first-episode drug-na{\"\i}ve schizophrenia: Associations with auditory hallucination.\emph{Human Brain Mapping} 41(8): 1973-1984. DOI: 10.1002/hbm.24923}

\cvitem{}{Zhang Y, Liu W, Lebowitz ER, Zhang F, Hu Y, Liu Z, Yang H, Wu J, Wang Y, Silverman WK, \textbf{\underline{Yang Z*}}, Cheng W* (2020). Abnormal asymmetry of thalamic volume moderates stress from parents and anxiety symptoms in children and adolescents with social anxiety disorder. \emph{Neuropharmacology} 180: 108301. DOI: 10.1016/j.neuropharm.2020.108301}

\cvitem{}{\textbf{\underline{Yang Z*}}, Wu J, Xu L, Deng Z, Tang Y, Gao J, Hu Y, Zhang Y, Qin S*, Li C, Wang J* (2020). Individualized psychiatric imaging based on inter-subject neural synchronization in movie watching. \emph{Neuroimage}: 116227. DOI:10.1016/j.neuroimage.2019.116227}

\cvitem{}{Cui H, Zhang B, Li W, Li H, Pang J, Hu Q, Zhang L, Tang Y, \textbf{\underline{Yang Z}}, Wang J, Li C*. (2020): Insula shows abnormal task-evoked and resting-state activity in first-episode drug-naïve generalized anxiety disorder. \emph{Depression and Anxiety} 37: 632–644. DOI: 10.1002/da.23009}

\cvitem{}{Deng Z, Wu J, Gao J, Hu Y, Zhang Y, Wang Y, Dong H, \textbf{\underline{Yang Z*}}, Zuo, X-N (2019). Segregated precuneus network and default mode network in naturalistic imaging. \emph{Brain Structure and Function} 224(9): 3133-3144. DOI: 10.1007/s00429-019-01953-2.}

\cvitem{}{Zhang Y, Xu Li, Hu Y, Wu J, Li C, Wang J*, \textbf{\underline{Yang Z*}} (2019). Functional connectivity between sensory-motor sub-networks reflects the duration of untreated psychosis and predicts treatment outcome of first-episode drug-na{\"\i}ve schizophrenia. \emph{Biological Psychiatry: Cognitive Neuroscience and Neuroimaging}. 4(8): 697-705}

\cvitem{}{Jiang L, Cao X, Jiang J, Li T, Wang J, {\underline{\textbf{Yang Z*}}}, Li C* (2019). Atrophy of hippocampal subfield CA2/3 in healthy elderly men is related to educational attainment. \emph{Neurobiology of Aging} 80: 21-28}

\cvitem{}{Hu Y, Du W, Zhang Y, Li N, Han Y*, \textbf{\underline{Yang Z*}} (2019). Loss of parietal memory network integrity in Alzheimer's disease. \emph{Frontiers in Aging Neuroscience} 11: 67}

\cvitem{}{Zhao Q, Xu T, Wang Y, Chen D, Liu Q, \textbf{\underline{Yang Z*}}, Wang Z*. (2019). Limbic cortico-striato-thalamo-cortical functional connectivity in drug-na{\"\i}ve patients of obsessive-compulsive disorder. \emph{Psychological Medicine} 49: 1156-1165. DOI: 10.1017/S0033291719002988}

\cvitem{}{Wang J, Hu Y, Li H, Ge L, Li J, Cheng L, \textbf{\underline{Yang Z*}}, Zuo XN, Xu Y* (2018). Connecting openness and the resting-state brain network: A discover-validate approach. \emph{Frontiers in Neuroscience} 12: 762.}

\cvitem{}{\textbf{\underline{Yang Z}}, Zuo XN*, McMahon KL, Craddock RC, Kelly C, de Zubicaray GI, Hickie I, Bandettini PA, Castellanos FX, Milham MP*, Wright MJ (2016). Genetic and environmental contributions to functional connectivity architecture of the human brain. \emph{Cerebral Cortex} 26: 2341-2352}

\cvitem{}{\textbf{\underline{Yang Z*}}, Qiu J, Wang P, Liu R, Zuo X* (2016). Brain structure-function associations identified in large-scale neuroimaging data. \emph{Brain Structure \& Function} 221: 4459-4474}

\cvitem{}{Hu Y, Wang J, Li C, Wang Y-S, \textbf{\underline{Yang Z*}}, Zuo X-N (2016). Segregation between the parietal memory network and the default mode network: effects of spatial smoothing and model order in ICA. \emph{Science Bulletin}. 61 (24): 1844-1854}

\cvitem{}{\textbf{\underline{Yang Z*}}, Huang Z, Gonzalez-Castillo J, Dai R, Northoff G, Bandettini P (2014). Using fMRI to decode true thoughts independent of intention to conceal. \emph{NeuroImage} 99: 80-92}

\cvitem{}{\textbf{\underline{Yang Z*}}, Chang C, Xu T, Jiang L, Handwerker D, Castellanos F, Milham M, Bandettini P, Zuo X* (2014). Connectivity trajectory across lifespan differentiates the precuneus from the default network. \emph{NeuroImage} 89: 45-56}

\cvitem{}{\textbf{\underline{Yang Z*}}, Zuo X, Wang P, Li Z, Laconte S, Bandettini PA, Hu X (2012). Generalized RAICAR: Discover homogeneous subject (sub)groups by reproducibility of their intrinsic connectivity networks. \emph{NeuroImage} 63: 403-414}

\cvitem{}{\textbf{\underline{Yang Z}}, Xu Y*, Xu T, Hoy C, Handwerker D, Chen G, Northoff G, Zuo X*, Bandettini P (2014). Brain network informed subject community detection in early-onset schizophrenia. \emph{Scientific Reports} 4: 5549}

\cvitem{}{\textbf{\underline{Yang Z}}, LaConte S, Weng X, Hu X* (2008). Ranking and averaging independent component analysis by reproducibility (RAICAR).  \emph{Human Brain Mapping} 29: 711-725}

\cvitem{}{Xu T, \textbf{\underline{Yang Z (co-first author)}}, Jiang L, Xing XX, Zuo XN* (2015). A connectome computation system for discovery science of brain. \emph{Science Bulletin} 60: 86-95}

\cvitem{}{\textbf{\underline{Yang Z*}}, Fang F, Weng X (2012). Recent developments in multivariate pattern analysis for functional MRI.  \emph{Neuroscience Bulletin} 28: 399-408}

\cvitem{}{\textbf{\underline{Yang Z*}}, Wu P, Weng X, Bandettini P (2014). Cerebellum engages in automation of verb-generation skill.  \emph{Journal of Integrative Neuroscience} 13: 1-17}

\cvitem{}{Liu C, Li F, Li S, Wang Y, Tie C, Wu H, Zhou Z, Zhang D, Dong J, \textbf{\underline{Yang Z*}}, Wang C* (2012). Abnormal baseline brain activity in bipolar depression: A resting-state functional magnetic resonance imaging study. \emph{Psychiatry Research: Neuroimaging} 203: 175-179}

\cvitem{}{Tang L, Liu C, Jing B, Ma X, Li H, Zhang Y, Li F, Wang Y, \textbf{\underline{Yang Z*}}, Wang C* (2014). Voxel-based morphometry study of the insular cortex in bipolar depression. \emph{Psychiatry Research: Neuroimaging} 224: 89-95}

\cvitem{}{Liu C, Ma X*, Wu X, Zhang Y, Zhou F, Li F, Tie C, Dong J, Wang Y, \textbf{\underline{Yang Z*}}, Wang C (2013). Regional homogeneity of resting-state brain abnormalities in bipolar and unipolar depression. \emph{Progress in Neuro-Psychopharmacology \& Biological Psychiatry} 41: 52-59}

\cvitem{}{\textbf{\underline{Yang Z}}, Zhao J, Jiang Y*, Li C, Wang J, Weng X*, Northoff G (2011). Altered negative Unconscious processing in major depressive disorder: An exploratory neuropsychological study.  \emph{PLoS One} 6: e21881}

\cvitem{}{Li W, Cui H, Zhu Z, Kong L, Guo Q, Zhu Y, Hu Q, Zhang L, Li H, Li Q, Jiang J, Meyers J, Li J, Wang J*, \textbf{\underline{Yang Z*}}, Li C* (2016). Aberrant functional connectivity between the amygdala and the temporal pole in drug-free generalized anxiety disorder. \emph{Frontiers in Human Neuroscience} 10: 549}

\cvitem{}{Sun L, Xu H, Zhang J, Li W, Nie J, Qiu Q, Liu Y, Fang Y, \textbf{\underline{Yang Z*}}, Li X* and Xiao S* (2018). Alcohol consumption and subclinical findings on cognitive function, biochemical indexes, and cortical anatomy in cognitively normal aging Han Chinese population. \emph{Frontiers in Aging Neuroscience} 10: 182}

\cvitem{}{Xu G, Jiang Y, Ma L, \textbf{\underline{Yang Z*}}, Weng X* (2012). Similar spatial patterns of neural coding of category selectivity in FFA and VWFA under different attention conditions. \emph{Neuropsychologia} 50: 862-868}

\cvitem{}{Huang Z, Zhang X, \textbf{\underline{Yang Z*}}, Dong G, Wu J, Chan A, Weng X (2010). Verbal memory retrieval engages visual cortex in musicians. \emph{Neuroscience} 168: 179-189}


%----------------------------------------------------------------------------------------
%	Publication
%----------------------------------------------------------------------------------------
\section{Teaching Experience}
\cventry{2024-2025}{Advances in Psychological Research}{Graduate course}{32 hours}{Capital Medical University}{}
\cventry{2022}{Functional Neuroimaging: Principles and Practice}{Graduate course}{32 hours}{Shanghai Jiao Tong University}{}
\cventry{2018-2022}{Introduction to Psychology}{Undergraduate course}{30 hours}{Shanghai Jiao Tong University}{}
\cventry{2008-2018}{Statistics for Psychology Research}{Graduate course}{60 hours}{Institute of Psychology, Chinese Academy of Sciences}{}
\cventry{2012-2018}{Advanced Statistics and Machine Learning}{Graduate course}{60 hours}{Institute of Psychology, Chinese Academy of Sciences}{}
\cventry{2008-2010}{Cognitive Neuroscience}{Graduate course}{60 hours}{Institute of Psychology, Chinese Academy of Sciences}{}
\cventry{2008-2018}{Brain Development and Learning}{Graduate course}{40 hours}{Institute of Psychology, Chinese Academy of Sciences}{}
\cventry{2015-2016}{Cognitive Neuroscience}{Graduate course}{48 hours}{University of Chinese Academy of Sciences}{}

%----------------------------------------------------------------------------------------
%   Examples
%----------------------------------------------------------------------------------------
%\renewcommand{\listitemsymbol}{-~}
%\cvlistitem{Quick Learner.}
%\cvlistitem{Able to handle multiple situations at the same time.}
%\cvlistitem{Easily Adaptable.}
%\cvlistitem{Can manage time effectively}
%\cvitemwithcomment{Hindi}{Intermediate}{Can understand good}
%\cvitemwithcomment{English}{Fluent}{Conversationally fluent}

%----------------------------------------------------------------------------------------
%	Award
%----------------------------------------------------------------------------------------

\section{Awards and Honors}

\cvitem{2025}{\textbf{Beijing High-Level Entrepreneurial and Innovative Talent Program — Summit Program}, Beijing Municipal Commission of Health}

\cvitem{2017}{\textbf{Second Prize in Science and Technology Progress Award}, Beijing Municipal Commission of Science and Technology}
\cvitem{2017}{\textbf{Chenguang Prize for Academic Excellency}, Shanghai Jiao Tong University}
\cvitem{2016}{\textbf{Elected Member of Youth Innovation Program}, Chinese Academy of Sciences}
\cvitem{2015}{\textbf{First Prize in Science and Technology Progress Award}, The Ministry of Education of China}
\cvitem{2015}{\textbf{Beijing Nova Program}, Beijing Municipal Commission of Science and Technology}
\cvitem{2014}{\textbf{Outstanding Young Investigator Award}, Institute of Psychology, Chinese Academy of Sciences}
\cvitem{2009--2011}{\textbf{Excellent Assistant Professor Award}, Institute of Psychology, Chinese Academy of Sciences}




%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

%\section{Interests}

%\renewcommand{\listitemsymbol}{-~} % Changes the symbol used for lists

%\cvlistdoubleitem{Driving}{Photography}
%\cvlistdoubleitem{Cooking}{Basket Ball}
%\cvlistitem{Cricket}
%\section{Personal Details}
%\cvitem{DOB}{04th of Feb, 1994}
%\cvitem{Address}{D.No:59-20-7/4B,APT Backside,kakinada-533002}
%\cvitem{Languages}{Telugu,Hindi,English}
%\cvitem{Mobile No.}{+91 9492390759}
%\section{References}
%\cvitem{Name}{K.Harish}
%\cvitem{Designation}{Senior Software Engineer}
%\cvitem{Organisation}{Happiest Minds-Bangalore}
%\cvitem{Ph No}{8105543434}
%\cvitem{Mai}{harish.kmail@gmail.com}


%----------------------------------------------------------------------------------------
%	COVER LETTER
%----------------------------------------------------------------------------------------

% To remove the cover letter, comment out this entire block

%\clearpage

%\recipient{HR Department}{Corporation\\123 Pleasant Lane\\12345 City, State} % Letter recipient
%\date{\today} % Letter date
%\opening{Dear Sir or Madam,} % Opening greeting
%\closing{Sincerely yours,} % Closing phrase
%\enclosure[Attached]{curriculum vit\ae{}} % List of enclosed documents

%\makelettertitle % Print letter title

%\lipsum[1-3] % Dummy text

%\makeletterclosing % Print letter signature

%----------------------------------------------------------------------------------------

\end{document}